\documentclass[11pt, English]{article}
\usepackage{graphicx}	
\usepackage{color, colortbl}
\definecolor{Orange}{rgb}{1.0,0.49,0.0}
\definecolor{brightyellow}{rgb}{1.0,0.67,0.11}
\usepackage {multirow}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage[left=0.7in, right=0.7in, top=0.7in, bottom=0.7in]{geometry}
\usepackage{longtable}

\newcommand{\VAR}[1]{}
\newcommand{\BLOCK}[1]{}													
\usepackage[]{color}
\usepackage[table,x11names]{xcolor}
\usepackage[font=bf]{caption}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\setlength{\aboverulesep}{0pt}
\setlength{\belowrulesep}{0pt}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tocloft,sectsty}


\begin{document}
\thispagestyle{empty}








\textbf{Standard:} MA 6.1.1 Numeric Relationships: Students will demonstrate, represent, and show relationships among fractions, decimals, percents, and integers within the base-ten number system.\\

\begin{longtable}{|p{11.0cm}|p{1.8cm}|p{3.7cm}|}

\hline


\rowcolor{Orange}
        \multicolumn{3}{|p{17.36cm}|}{\textbf{MA 6.1.1.a Determine common factors and common multiples using prime factorization of numbers with and without exponents.}}\\
        \hline
        \rowcolor{brightyellow}
        \hfil{ALD Level Descriptions}&\hfil{Maximum DOK}&\hfil{Aligned Item Formats}\\
        \hline

\endfirsthead
\multicolumn{3}{@{}l}{\ldots continued}\\\hline



\rowcolor{Orange}
        \multicolumn{3}{|p{17.36cm}|}{\textbf{MA 6.1.1.a Determine common factors and common multiples using prime factorization of numbers with and without exponents.}}\\ 
        \hline
        \rowcolor{brightyellow}
        \hfil{ALD Level Descriptions}&\hfil{Maximum DOK}&\hfil{Aligned Item Formats}\\
        \hline

\endhead % all the lines above this will be repeated on every page
\hline

\multicolumn{3}{r@{}}{continued \ldots}\\
\endfoot
\hline
\endlastfoot 



\textbf{Level 1 Developing}\newline
• Identifies the prime factorization for a whole number less than 100 without exponents.\newline• Identifies common multiples for a given pair of prime numbers. \newline
& \hfil{1}
&• Gap Match or Graphic Gap Match\newline• Multiple Choice or Choice Multiple\\
\hline




\textbf{Level 2 On Track}\newline
• Determines the prime factorization for a whole number less than 100 with exponents. \newline• Determines the prime factorization for a whole number greater than 100 with or without exponents. \newline• Determines either common factors or common multiples for two whole numbers both less than 100 when presented with or without their prime factorization. If provided, the prime factorization can be with or without exponents. At least one of the numbers should be a composite number. \newline

 & \hfil{1}
 &• Gap Match or Graphic Gap Match\newline• Graphing\newline• Multiple Choice or Choice Multiple\newline• Text Entry\\
\hline


 
\textbf{Level 3 College and Career Ready}\newline
• Determines common factors and common multiples for two whole numbers both less than 100 when presented with or without their prime factorization. If provided, the prime factorization can be with or without exponents. At least one of the numbers should be a composite number. \newline• Determines the greatest common factor or least common multiple for two whole numbers presented with or without their prime factorization. If provided, the prime factorization can be with or without exponents. \newline• Determines common factors or common multiples for two whole numbers with at least one greater than 100 when presented with or without their prime factorization. If provided, the prime factorization can be with or without exponents. At least one of the numbers should be a composite number. \newline

& \hfil{1}
&• Gap Match or Graphic Gap Match\newline• Graphing\newline• Multiple Choice or Choice Multiple\newline• Text Entry\\
\hline 


\end{longtable}











\end{document}